### 2009-01-26 articles/2009/geoinformatics/article.tex
Initial edits by Tim
git-svn-id: https://svn.osgeo.org/qgis/trunk@10015 c8812cc2-4d05-0410-92ff-de0c093fc19c

Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS).
It is written in C++ and Python with a QT based GUI. It is licensed under the
GNU General Public License (GPL) and an official project of the Open Source
Geospatial Foundation (OSGeo). The current stable version 1.0 was released in
January 2009.

@@

The QGIS project is carried out largely by a group of dedicated developers,
translators, documenters, release helpers, bug reporters, and promoters. It
is managed by the Project Steering Committee (PSC), a five member committee
providing technical guidance, community liason, release management, and
financial/marketing activities. The work of the QGIS project process is
spread between numerous people who each have a specific area of
resposibility.

All these volunteers together with a large number of users make up the
world-wide QGIS comunity, which in time has built up a comprehensive,
valuable and useful code and documentation base free to use and improve for
everybody.

@@

With community platforms such as website, wiki, and blog the QGIS project
provides latest news, release, usage, and development information and also
allows own contributions after subscription. A prefered first step to contact
other users for discussions of QGIS in general, as well as specific questions
regarding its installation and use is by joining the qgis-user mailing list,
the QGIS Forum or the Internet Relay Chat (IRC).

@@

QGIS offers a growing number of common GIS functionalities provided by core
features and plugins. They are presented in a friendly graphical user
interface, clearly seperated in menu bar, tool bar, status bar, map view,
overview, and map legend (see Figure~\ref{fig:qgis10}).

@@

The menu and tool bar give access to all QGIS features and at a glance
provide following features:

@@

Otto Dassau <dassau@nature-consult.de>  
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfinity.com>
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
\\Paolo Cavallini <cavallini@faunalia.it>

>>>>

Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS).
It is written in C++ and Python with a Qt4 based GUI. It is licensed under the
GNU General Public License (GPL) and an official project of the Open Source
Geospatial Foundation (OSGeo). The current stable version 1.0 was released in
January 2009.

@@

The QGIS project is the work of a group of dedicated developers,
translators, documenters, release helpers, bug reporters, and promoters. Their 
contributions are mainly on a voluntary basis, except in a few cases where 
contributors are able to work on QGIS as part of their daily work. QGIS 
is managed by the Project Steering Committee (PSC), a five member committee
providing technical guidance, community liason, release management, and
financial/marketing activities. The work of the QGIS project process is
spread between numerous people who each have a specific area of
resposibility, and ad hoc contributors.

These volunteers together with a large number of users make up the
world-wide QGIS comunity. Over time their efforts have resulted in a comprehensive,
valuable and useful code and documentation base which is free for everyone 
to use and improve on.

@@

With community platforms such as our website, wiki, forums and blog the QGIS project
provides latest news, release, usage, and development information. In most cases 
these community web sites permit user contributions after registering. 
The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable interface 
with other users and for discussions of QGIS in general. In the spirit of open 
process and sharing knowledge, contacting developers directly instead of going through 
these community based avenues of communication is frowned apon.

@@

QGIS offers a growing number of common GIS functionality provided by core
features and plugins. They are presented in a friendly graphical user
interface, clearly seperated into a menu bar, tool bars, status bar, map view,
overview, and map legend (see Figure~\ref{fig:qgis10}).

@@

The menu and tool bars give access to all QGIS features and at a glance
provide following features:

@@

Otto Dassau <dassau@nature-consult.de>  
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
\\Paolo Cavallini <cavallini@faunalia.it>
